### 2023-10-26 results/airline.tex
Morning writing

@@

@@

@@

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \multirow{2}{*}{\acs{RMSE}} & \multicolumn{3}{|c|}{Analog prediction}\\
    \cline{2-4}
    & $n_s=1$ & $n_s=2$ & $n_s=4$ \\
    \hline
    \specialcell{Digital prediction with\\default activation functions} & $141$ & $144$ & $140$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each analog prediction to their associated digital prediction}
  \label{tab:airlineAnalogNoC}
\end{table}

@@

@@

Once again, the results are quite close to each others, but as expected the errors (\cref{tab:airlineAnalogError}) are higher then the ones found in \cref{tab:airlineAnalogNoCZoomed}. The farthest appart ($n_s=1$ to $n_s=2$ with an error of $64.61$ thousands passengers) have an error barely higher than the error of digital results to the target dataset (\cref{tab:airlineDigital})

@@

>>>>

The same network configuration using a \ac{GRU} layer instead of an \ac{LSTM} layer. The number of hidden states is the same.

@@

\subsubsection{\acs{LSTM} predictions}

@@

\subsubsection{\acs{GRU} predictions}

Unlike for the predictions using an \ac{LSTM} layer, the weights were only trained using the analog activation functions. The effect of using the default activation functions is already shown with the \ac{LSTM} layer.

The graph of the resulting prediction is the one in \cref{graph:airlineDigitalGRU}, the error rate is also in the figure.

Interestingly, the results look much better when using the \ac{GRU} layer. The error rate confirms that as it is almost half of what it was with the \ac{LSTM} layer (\cref{tab:airlineDigital}). That simply means that the \ac{GRU} layer is better at handling this problem, as was previously stated in \cref{sec:gru}.

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{datasets/airlineDigitalGRU}
  \caption{Graph of the digital predictions along with the \ac{RMSE} for the airline dataset using a \ac{GRU} layer. The dotted vertical line shows the limit of the data used for training and the one used for validation.}
  \label{graph:airlineDigitalGRU}
\end{figure}

@@

The \ac{LSTM} layer being the only to have been trained using the default activation functions the only results presented here are using an \ac{LSTM} layer.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    \multirow{2}{*}{\acs{RMSE}} & \multicolumn{3}{c|}{Analog prediction}\\
    \cline{2-4}
    & $n_s=1$ & $n_s=2$ & $n_s=4$ \\
    \hline
    \specialcell{Digital prediction with\\default activation functions} & $141$ & $144$ & $140$\\
    \hline
  \end{tabular}
  \caption{\acp{RMSE} of each analog prediction to their associated digital prediction}
  \label{tab:airlineAnalogNoC}
\end{table}

@@

\subsubsection{\ac{LSTM} predictions}

@@

Once again, the results are quite close to each others, but as expected the errors (\cref{tab:airlineAnalogError}) are higher then the ones found in \cref{tab:airlineAnalogNoCZoomed}. The farthest appart ($n_s=1$ to $n_s=2$ with an error of $64.6$ thousands passengers) have an error barely higher than the error of digital results to the target dataset (\cref{tab:airlineDigital})

@@

\subsubsection{\ac{GRU} predictions}

Like explained in \cref{sec:gruCircuit}, the \ac{GRU} layer cannot be serialized in an analog circuit. The simulation were only ran once, for the only version available.

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/airline/analogGRU}
  \caption{Analog prediction of the \ac{GRU} analog circuit}
  \label{graph:airlineAnalogGRU}
\end{figure}

\Cref{graph:airlineAnalogGRU} contains the analog predcitions of the \ac{GRU} circuit. The results are even worse than the results of simulation using weights generated with the default activation functions. Indeed, the error rate found in \cref{graph:airlineAnalogGRU} is much greater than the ones in \cref{tab:airlineAnalogNoC}. This means that while the circuit produces the right output shape, there is something wrong with the current version of the circuit.

### 2023-10-26 state/gru.tex
Morning writing

The \ac{GRU} is very often compared to the \ac{LSTM}, being sometimes assimilated as a type of \ac{LSTM} \cite{nbLSTM}. Their performance was found to be very similar in most situations, making those two types of \acp{RNN} coexistant in the modern machine learning world.

>>>>

The \ac{GRU} is very often compared to the \ac{LSTM}, being sometimes assimilated as a type of \ac{LSTM} \cite{nbLSTM}. Their performance was found to be very similar in most situations \cite{gruVSlstm}, making those two types of \acp{RNN} coexistant in the modern machine learning world.
